Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-09 Paper/paper.tex
Abstract and Intro edits

%%%%%%%%%%%%%%%%
%%% Abstract 
%%% VERY General overview of problem and solution in paper
%%%%%%%%%%%%%%%%
\begin{abstract}
Web applications are quickly replacing standalone applications for everyday tasks. These web applications need to be tested to ensure proper functionality and reliability. There have been substantial efforts to create tools that assist with the testing of web applications but there is, as of yet, no standard set of tools or a recommended workflow to ensure speed of development and strength of application.

We have used and outlined the merits of a number of existing testing tools and brought together the best among them to create what we feel is a fully-featured, easy to use, testing framework and workflow for web applications.

@@

Many of these tools are targeted at solving one or two phases of the testing cycle but do not cover all phases. In addition, some of the tools overlap or require tight coupling that prevents them from being used in combination with one another. Having to wade through a sea of similar tools or try to force tools to work together is time-consuming, which can be the death of a cutting-edge application. The more time an application is off the market, the more time competitors have to develop their own versions. Yet another problem is that deciding between similar tools can be discouraging to the developer that just wants to write their application and test it quickly.

Even the tools that already exist suffer from additional problems regarding their stages of development and amount of support. As will be discussed later, we've found tools that are in their beta stages that show incredible promise as well as mature tools that are widely used that leave much to be desired. These problems effect both industry tools as well as independent developers.

There needs to be a framework in place for testing these multi-layer, multi-faceted web applications that is easy to use, allows for quick development, and is thorough in its coverage. This thesis will explore some of the most popular tools with the end goal being to gather the best tools out there and collect them in one place. We will attempt to gather tools that work well together and cover all phases of the testing cycle for an average developer, particular a developer who has experience in some field of software but may be new to web applications. Our hope is that this thesis will serve as a starting point and guide to future web application developers.

@@

In the very beginning, web applications were easy to write and test because the only code was plain HTML with a common set of HTML tags. It didn't matter what browser was used to view the content because the viewer was always a home computer rendering plain HTML. As time progressed individual browsers began offering additional features and web applications became more rich but harder to test because the developer would need to run their code on multiple browsers to make sure they all behaved similarly. In today's technological world, it is nearly impossible to run one's web application on all of the possible browser versions, configurations, and platforms that are available. Web applications are on home computers, phones, tablets, MP3 players, refrigerators \cite{SamsungFridge}, and a variety of other devices of varying sizes and capabilities. As a developer, one wants to target as many of those platforms as possible with a single code-base to save time and effort. A naive developer might just release an application on all platforms and hope for the best, but releasing on all platforms without testing will likely drive consumers away if the application fails on their given platform.

% - Asynchronous shennanigans
The addition of JavaScript to web applications led to a golden age of feature-rich applications with exciting user interface (UI) features that had not before been seen. This set of features and UI improvements came with the complication of asynchronous execution. Unlike traditional multi-threaded software, however, the developer is not given access to individual threads, they only have access to the main thread. This sort of implementation is essential for dealing with asynchronous events like button clicks, loading data separately so as not to hold up the web page, and a variety of other niceties, but is the cause of major headaches in testing. Without access to individual threads, the developer has to either write synchronous code that will be slow and not user-friendly, or rely on other mechanisms that allow code to be sequenced. Often it is hard to get code properly sequenced and it requires changing straightforward functions to a hideous amalgamation of callbacks.

>>>>

%%%%%%%%%%%%%%%%
%%% Abstract 
%%% VERY General overview of problem and solution in paper
%%%%%%%%%%%%%%%%
\begin{abstract}
Web applications are quickly replacing standalone applications for everyday tasks. These web applications need to be tested to ensure proper functionality and reliability. There have been substantial efforts to create tools that assist with the testing of web applications, but there is no standard set of tools or a recommended workflow to ensure speed of development and strength of application.

We have used and outlined the merits of a number of existing testing tools and brought together the best among them to create what we feel is a fully-featured, easy to use, testing framework and workflow for web application development.

@@

Many of these tools are targeted at solving one or two aspects of complete testing but do not cover everything. In addition, some of the tools overlap or require tight coupling that prevents them from being used in combination with one another. Having to wade through a sea of similar tools or try to force tools to work together is time-consuming, which can be the death of a cutting-edge application. The more time an application is off the market, the more time competitors have to develop their own versions. Yet another problem is that deciding between similar tools can be discouraging to the developer that just wants to write their application and test it quickly.

Even the tools that already exist suffer from additional problems regarding their stages of development and amount of support. As will be discussed later, we've found tools that are in their beta stages that show incredible promise as well as mature tools that are widely used but leave much to be desired. These problems effect both industry tools as well as independent developers.

There needs to be a framework in place for testing these multi-layer, multi-faceted web applications that is easy to use, allows for quick development, and is thorough in its coverage. This thesis will explore some of the most popular tools with the end goal of gathering the best tools out there and collecting them in one place. We will attempt to gather tools that work well together and cover all aspects of testing for an average developer, particular a developer who has experience in some field of software but may be new to web applications. Our hope is that this thesis will serve as a starting point and guide to future web application developers.

@@

In the very beginning, web applications were easy to write and test because the only code was plain HTML with a common set of HTML tags. It did not matter what browser was used to view the content because the viewer was always a home computer rendering plain HTML. As time progressed, individual browsers began offering additional features and web applications became more rich but harder to test because the developer would need to run their code on multiple browsers to make sure they all behaved similarly. In today's technological world, it is nearly impossible to run one's web application on all of the possible browser versions, configurations, and platforms that are available. Web applications are on home computers, phones, tablets, MP3 players, refrigerators \cite{SamsungFridge}, and a variety of other devices of varying sizes and capabilities. As a developer, one wants to target as many of those platforms as possible with a single code-base to save time and effort. A naive developer might just release an application on all platforms and hope for the best, but releasing on all platforms without testing will likely drive consumers away if the application fails on their given platform.

% - Asynchronous shennanigans
The addition of JavaScript to web applications led to a golden age of feature-rich applications with exciting user interface (UI) features that had not before been seen. This set of features and UI improvements came with the complication of asynchronous execution. Unlike traditional multi-threaded software, however, the developer is not given access to individual threads, they only have access to the main thread. This sort of implementation is essential for dealing with asynchronous events like button clicks, loading data separately so as not to hold up the web page, and a variety of other niceties, but is a cause of major headaches in testing. Without access to individual threads, the developer has to either write synchronous code that will be slow and not user-friendly, or rely on other mechanisms that allow code to be sequenced. Often it is hard to get code properly sequenced and it requires changing straightforward functions to a hideous amalgamation of callbacks.
